Numerical simulation of the Cordilleran ice sheet through the last glacial cycle

### 2014-06-17 cordillera-cycle.tex
Add EPICA run deglaciation profiles.

On the Interior Plateau of British Columbia, modelled deglaciation consists of
a rapid northwards retreat, leaving a slow-flowing ice lobe on the
plateau, while the surrounding mountain ranges are already deglaciated
(Fig.~\ref{fig:profiles}). Although this supports the top-down (?)
deglaciation hypothesis for central British Columbia, modelled, southwards,
last flow directions do not agree with the local lineation patterns
(Fig.~\ref{fig:lastflow}). This could indicate that the lineations are older,
or that the modelled last glacial maximum ice sheet is too extensive to the
east, resulting in modelled deglaciation flow patterns different from those
observed in the geomorphology.

@@

% fig:profiles
\begin{figure}
  \includegraphics{profiles}
  \caption{Modelled bedrock (black) and ice surface (blue) topography profiles
           during deglaciation (22.0--8.0\,kyr) in the GRIP 6\,km
           simulation, corresponding to the four transects indicated in
           Fig.~\ref{fig:deglac}.
           \note{should we have a similar figure using EPICA?}}
  \label{fig:profiles}
\end{figure}

>>>>

On the Interior Plateau of British Columbia, modelled deglaciation consists of
a rapid northwards retreat, leaving a slow-flowing ice lobe on the
plateau, while the surrounding mountain ranges are already deglaciated
(Figs.~\ref{fig:profiles-grip} and~\ref{fig:profiles-epica}). Although this
supports the top-down (?)
deglaciation hypothesis for central British Columbia, modelled, southwards,
last flow directions do not agree with the local lineation patterns
(Fig.~\ref{fig:lastflow}). This could indicate that the lineations are older,
or that the modelled last glacial maximum ice sheet is too extensive to the
east, resulting in modelled deglaciation flow patterns different from those
observed in the geomorphology.

@@

% fig:profiles-grip
\begin{figure}
  \includegraphics{profiles-grip}
  \caption{Modelled bedrock (black) and ice surface (blue) topography profiles
           during deglaciation (22.0--8.0\,kyr) in the GRIP 6\,km
           simulation, corresponding to the four transects indicated in
           Fig.~\ref{fig:deglac}.}
  \label{fig:profiles-grip}
\end{figure}

% fig:profiles-epica
\begin{figure}
  \includegraphics{profiles-epica}
  \caption{Modelled bedrock (black) and ice surface (blue) topography profiles
           during deglaciation (22.0--8.0\,kyr) in the EPICA 6\,km
           simulation, corresponding to the four transects indicated in
           Fig.~\ref{fig:deglac}.}
  \label{fig:profiles-epica}
\end{figure}
